---
title: "Class 11 - Scraping Multiple Webpages"
author: "Joseph Sher"
date: "2026-09-30"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    numbered_sections: TRUE
    code_download: TRUE
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives

- Enable you to scrape multiple webpages from the same site using a `for` loop type approach
- Enable you to scrape multiple webpages from the same site, using the [purrr package](https://purrr.tidyverse.org/), which is a functional programming approach.
*Note:* In this process, we will create our own function.


# Re-Examining the Bulletin Example

Let us try to expand on the example from the last class to include the following:
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/)
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/)
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/), and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/)

*Comment:* You can repeat your code a few times with changing the URL. This will work for a few links but would be quite tedious for large amounts of scraping. We will follow the **DRY Principle** which stands for *Don't Repeat Yourself*

```{r bulletin}
dept_abbr = c('acc','bus','isa','mkt')
courses_df = data.frame() # Initializing a container to store stuff in from the loop
for(abbrv in dept_abbr){
  cat(rep("-",50),"\n")
  print(abbrv)
  bulletin_url = paste0("https://bulletin.miamioh.edu/courses-instruction/",abbrv,'/')

# We did this so we could reuse the rest of your code with only changing the URL

webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("strong")|> rvest::html_text2() -> titles
webpage |> rvest::html_elements(" p.courseblockdesc") |> rvest::html_text2() -> descs

df=data.frame(title=titles, description = descs)
print(df$title[1:2])
courses_df = rbind(courses_df, df)
}





```

## `purr` approach for the same problem

This is a functional programming approach, and we will write our own function. In R, we use a function called `function` to create a function. As opposed to Python, R functions return a single object.

```{r purr}
dept_abbr = c('acc','bus','isa','mkt')

#This function takes an abbreviation as an input, and returns a data_frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0("https://bulletin.miamioh.edu/courses-instruction/",abbrv,'/')

# We did this so we could reuse the rest of your code with only changing the URL

webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("p.courseblocktitle")|>rvest::html_text2() -> titles
webpage |> rvest::html_elements(" p.courseblockdesc") |> rvest::html_text2() -> descs

df=data.frame(title=titles, description = descs)
return(df)
}


test = scrape_mu_bulletin(abbrv = 'eco')

# to use functions from purrr, we will use a map_*(), or a map2_*(), or a pmap_*()
# map uses a function that takes a single input (or you are only changing a single input)
# map2 uses a function that takes 2 inputs
#pmap >= 3
# after the _, you put the object you are getting back

# the .x is the vector that we will iterate over
# and the .f is the function we use

courses_df_from_purrr = purrr::map_df(.x = dept_abbr, .f= scrape_mu_bulletin)

```


# Scrape data from the website planecrashinfo
The website that we want to scrape is called: <https://www.planecrashinfo.com/> and it contains a database of plane crashes by year.

```{r}
year = 2025

crash_url = paste0("https://www.planecrashinfo.com/",year,'/',year,'.htm')

crash_page = rvest::read_html(crash_url)

```

